\chapter{Results}	\label{ch:results}
\glsresetall
The following sections show a comprehensive solver validation using various test cases presented in increasing levels of complexity. The tests also allow to highlight some of the benefits of the DG-method and the algorithms introduced before in this work, namely the globalized Newton method, homotopy strategy and the initialization of combustion applications using flame sheet estimates. 

First, in \cref{sec:SingleCompIsotCase} the applicability of the solver is analyzed for isothermal single-component systems. Later in \cref{sec:SinCompNonIsothermCase} several single-component non-isothermal configurations are studied. Finally, in \cref{sec:MultCompNonIsothermCase} test cases for multicomponent non-isothermal systems are presented, with a particular emphasis on systems where combustion is present.
%Additionally the convergence properties of the DG-method will be analyzed for some of the systems.

All calculations shown here were performed on a cluster with the following speficiations.
\begin{itemize}
    \item \textbf{CPU} 4x8 cores (Intel(R) Xeon(R) CPU E5-4627 v2)
    \item \textbf{CPU vector extension} Intel® AVX
    \item \textbf{CPU speed} basis 3.30 GHz, turbo 3.6 GHz
    \item \textbf{memory} 512 GByte (DDR3-1600)
\end{itemize}
Unless otherwise stated, all calculations use the termination criteria presented in \cref{ssec:TerminationCriterion}.
Some of the results presented in the next sections has been published \parencite{gutierrez-jorqueraFullyCoupledHighorder2022}.
%%%%%%%%
%%%%%%%%
\section{Single-component isothermal cases}\label{sec:SingleCompIsotCase}
%%%%%%%%
%%%%%%%%
The XNSEC solver presented in the previous chapter is validated first for single-component isothermal cases. In these cases, only the continuity and momentum equations are solved. The energy equation and the species concentration equations are replaced by the conditions $T = 1.0$ and $Y_0 = 1.0$ in the entire domain. This means that the physical properties of the flow (density and viscosity) are constant and that the flow is fully incompressible because the density does not show a thermodynamic or hydrodynamic dependence.
\input{chapters_main/results/SingleComponentIsotermal/LidDrivenCavity}
\input{chapters_main/results/SingleComponentIsotermal/BackwardFacingStep}
%%%%%%%%
%%%%%%%%
\section{Single-component non-isothermal cases} \label{sec:SinCompNonIsothermCase}
%%%%%%%%
%%%%%%%%
For the test cases presented in this section, the equations for continuity, momentum and energy are solved. All systems are assumed to be single-component, thus $N = 1$ and $Y_0 = 1.0$. 
The tests shown in this section shall serve as a throughout validation of the XNSEC solver spatial and temporal discretization for low-Mach variable density flows. 

First in \cref{ssec:HeatedBackwardFacingStep} an extension of the backward-facing step configuration for a non-isothermal system is shown, and benchmark values are compared to references. Later in \cref{ssec:CouetteFlowTempDiff} a Couette flow configuration that presents a temperature gradient in the vertical direction is studied and compared to an analytical solution. Additionally the numerical accuracy of the solver is shown and compared to calculations using a SIMPLE-type algorithm. Later in \cref{ss:DHC} a heated square cavity configuration is studied to assess the solver's ability to simulate steady state flow configurations of variable density in closed systems. In \cref{ssec:FlowCircCyl} the flow over a heated cylinder is studied, which serves as a test for unsteady calculations of non-isothermal systems. Finally in \cref{ssec:RayBer} a classical Rayleigh-Bénard convection system is treated, showing the behavior of the solver for unstable systems.
\input{chapters_main/results/SingleComponentNonIsotermal/HeatedBackwardFacingStep}
\input{chapters_main/results/SingleComponentNonIsotermal/CouetteTemperatureGradient}
\input{chapters_main/results/SingleComponentNonIsotermal/DifferentiallyHeatedCavity}
\input{chapters_main/results/SingleComponentNonIsotermal/FlowOverHeatedCylinder}
\input{chapters_main/results/SingleComponentNonIsotermal/RayleighBenardConvection}
%%%%%%%%
%%%%%%%%
\section{Multi-component non-isothermal cases}\label{sec:MultCompNonIsothermCase}
%%%%%%%%
%%%%%%%%
Finally in this section, test cases where the whole operator presented in \cref{ch:NumericalMethods} is used are shown. The balance equations of continuity, momentum, energy and species are considered and solved in a coupled manner, together with a equation of state and expressions for the transport parameters. For all the cases treated here, the solution of the flame sheet problem described in \cref{sec:FlameSheet} is calculated first, and then this solution is used as an initial estimate for the solution of the finite chemistry rate problem (see \cref{ssec:NonDimLowMachEquations}). For all test cases presented in this section, a smoothing parameter $\sigma = 40$ is used (see \cref{ssec:MethodCombustion}). 

As already mentioned before, for the resolution of the linear solver using a direct solver such as \textit{PARDISO} was not possible, because the memory requirements are too high. In all calculations of this section the multigrid orthonormalization method commented in \cref{ssec:LinearSolver} is used.

The combustion model used is the one-step model shown in \cref{sec:GovEqLowMach}. All calculations assume methane as fuel, therefore, the relevant chemical components are \ch{CH4}, \ch{O2}, \ch{CO2}, \ch{H2O} and \ch{N2}, thus $N = 5$ and $\vec{Y}' = \left(Y_{\ch{CH4}},Y_{\ch{O2}},Y_{\ch{CO2}},Y_{\ch{H2O}}\right)$. The nitrogen mass fraction $Y_{\ch{N2}}$ is calculated according to \cref{eq:MassFractionConstraint}.%

First in \cref{ssec:coflowFlame} a coflow laminar diffusion flame configuration is calculated and some remarks about the convergence behavior of the XNSEC solver using are made. Next in \cref{ss:CDF} a diffusion flame in a two-dimensional counterflow configuration is simulated and compared with results from a one-dimensional configuration solved using a fourth-order finite difference solver. Finally in \cref{ss:UDF} the convergence rates of the fully coupled solver are investigated by studing a pseudo-one-dimensional diffusion flame configuration.

\input{chapters_main/results/MultiComponentNonIsothermal/CoflowFlame}
\input{chapters_main/results/MultiComponentNonIsothermal/CounterflowDiffusionFlame}
\input{chapters_main/results/MultiComponentNonIsothermal/ChamberedDiffFlame}
\input{chapters_main/results/MultiComponentNonIsothermal/CombustionOverCylinder}
\FloatBarrier