\chapter*{Acknowledgements}
First of all, I would like to thank my supervisor Prof. Oberlack for his support and giving me the opportunity of writing this thesis at the Department of Fluid Dynamics. I would also like to express my gratitude to Florian Kummer, without whom the development of this work would not have been possible. 

Furthermore, I would like to thank all colleagues whom I had the privilege of working with over the four years I was in the Fluid Mechanics Department, sharing not only knowledge and scientific discussions, but also activities outside the office, nice coffee breaks, and visits to the Biergarten. In particular, I would like to thank (in alphabetical order) my colleagues Lauritz Beck, Anne Kikker, Dario Klingenberg, Matthias Rieckmann, Markus Geisenhofer and Jens Weber for their support in developing this thesis, along with the extensive and fruitful discussions we engaged in over the years.

I would like to extend my gratitude to my dear friends Anastasia, Andres, Francisco, Graziella, Javiera, Juan, Victor and the \textit{Diuquers} for their unconditional help during all these years. I truly believe that their support and company during difficult and joyful times was indispensable for the creation of this work. 

Last but not least, I want to express my gratitude to my sisters Catalina and Constanza, and to my parents, Juan Carlos and Margarita, since without them there would be no way for me to be where I am now. Their love and support in every way is something for which I will be eternally grateful.